Electric Power Consumption  - Exploratory
========================================================

This file is *not* the assignment - this is my working draft of the components that will go into the final assignment submission.

We only care about two days worth of data. I thought it was a lot simpler to pull the data out from the unzipped text file using shell script, and then import the data.

But in keeping with the code I eventually wrote for the plot scripts, I'll just pull it in and
reuse it that way.
 
```{r}
source(file="LoadAndPrepInput.R")
```

Here is the codebook for the data:

1. Date: Date in format dd/mm/yyyy
2. Time: time in format hh:mm:ss
3. Global_active_power: household global minute-averaged active power (in kilowatt)
4. Global_reactive_power: household global minute-averaged reactive power (in kilowatt)￼￼￼￼￼￼￼￼￼￼￼
5. Voltage: minute-averaged voltage (in volt)
6. Global_intensity: household global minute-averaged current intensity (in ampere)
7. Sub_metering_1: energy sub-metering No. 1 (in watt-hour of active energy). It corresponds to the
kitchen, containing mainly a dishwasher, an oven and a microwave (hot plates are not electric but
gas powered).
8. Sub_metering_2: energy sub-metering No. 2 (in watt-hour of active energy). It corresponds to the
laundry room, containing a washing-machine, a tumble-drier, a refrigerator and a light.
9. Sub_metering_3: energy sub-metering No. 3 (in watt-hour of active energy). It corresponds to an
electric water-heater and an air-conditioner.

Finally we have something we can look at, let's start with the summary data
```{r}
summary(hpc)
```

Now we can get to plotting something.

First one is power frequency histogram.

```{r,fig.width=10,fig.height=8}
hist(hpc$Global_active_power,xlab="Global Active Power (kilowatts)", ylim=c(0,1200), col="red",
     main='Global Active Power')
```

Next one is global active power per day.

```{r,fig.width=10,fig.height=8}
# earlier experiment
#hpc$weekday <- weekdays(hpc$datetime,abbreviate=TRUE)
#hpc$weekday <- as.factor(hpc$weekday)
#powday <- aggregate(hpc$Global_active_power,by=list(hpc$weekday),sum)

with(hpc, plot(x=DateTime, y=Global_active_power,type="l",xlab="", ylab="Global Active Power (kilowatts)"))

```

Next one is sub-metering levels per day, one line each.

```{r,fig.width=10,fig.height=8}
with(hpc, plot(x=DateTime, y=Sub_metering_1,type="l",xlab="", ylab="Energy sub metering"))
with(hpc, lines(x=DateTime,y=Sub_metering_2,col="red"))
with(hpc, lines(x=DateTime,y=Sub_metering_3,type="l",col="blue"))
with(hpc, legend("topright", 
                 legend=c("Sub_metering_1","Sub_metering_2","Sub_metering_3"), 
                 col=c("black","red","blue"), lty=1 ))
```

Last one is a 2x2 layout of:
power per day, voltage per day
sub-meters per day, reactive power per day

```{r,fig.width=10,fig.height=10}
par(mfrow=c(2,2))
# TODO make a function to factor out out the common elements here
#for now just copy from previous graphs, global active power
# note this one is subtly different on the ylabel - no units declared now
with(hpc, plot(x=DateTime, y=Global_active_power,type="l",xlab="", ylab="Global Active Power"))

# second graph also uses a simple xlabel, make sure its there
with(hpc, plot(x=DateTime, y=Voltage,type="l",xlab="datetime", ylab="Voltage"))

#third graph is just sub-metering again (but no box around the legend)
with(hpc, plot(x=DateTime, y=Sub_metering_1,type="l",xlab="", ylab="Energy sub metering"))
with(hpc, lines(x=DateTime,y=Sub_metering_2,col="red"))
with(hpc, lines(x=DateTime,y=Sub_metering_3,col="blue"))
with(hpc, legend("topright", bty="n",
                 legend=c("Sub_metering_1","Sub_metering_2","Sub_metering_3"), 
                 col=c("black","red","blue"), lty=1 ))

# last graph is reactive-power version of the first graph,different labeling again
with(hpc, plot(x=DateTime, y=Global_reactive_power,type="l",xlab="datetime"))

```

